Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-07-29 docs/comments/comments.tex
added IFC mechanisms and frameworks to address the 3rd comment of R2 and R3 respectively
As a result, the Observations section, Figure 2 and Figure 3 were
updated too.

\IEEEtitleabstractindextext{
\begin{abstract}
Some of the most dangerous web attacks, such as Cross-Site
Scripting and {\sc sql} injection, exploit vulnerabilities
in web applications that may accept and process
data of uncertain origin without proper validation or
filtering, allowing the injection and execution of
dynamic or domain-specific language code.
These attacks have been constantly topping the lists of
various security bulletin providers despite the numerous
countermeasures that have been proposed over the past 15 years.
In this paper, we provide an analysis on
various defense mechanisms against web code injection attacks.
We propose a model that highlights the key weaknesses enabling these attacks,
and that provides a common perspective for studying the available defenses.
We then categorize and analyze a set of 35 previously proposed defenses 
based on their accuracy, performance,
deployment, security, and availability characteristics.
Detection accuracy is of particular importance,
as our findings show that many defense
mechanisms have been tested in a poor manner. In addition, we observe
that some mechanisms can be bypassed by attackers with knowledge
of how the mechanisms work. Finally, we discuss the results
of our analysis, with emphasis on factors that may hinder
the widespread adoption of defenses in practice.
\vspace{-3mm}
\end{abstract}

@@

\noindent
{\bf Comment 2:} ``Admittedly, transition
from scientific research to real product
is challenging due to availability, usability,
performance and deployment issues.
Except for that, the paper does not thorouly
discuss why many previous works
cannot stop attacks against web applications,
nor provide useful guidance on
how future research could improve upon existing works.
Are there any fundamental
limitations in previous works that make
them not suitable for defending against
some specific (if not all) attacks?
Can we integrate multiple solutions to build
stronger defense mechanisms?"\\

@@

@@

\noindent
{\bf Comment 2:} ``Similarly, {\sc xss} is introduced
as an attack that has two forms,
reflected and persistent.
However,
even though it's mentioned later on,
how would {\sc dom}-based {\sc xss} fit into this breakdown?
I don't believe it does (neatly),
and am of the view that it constitutes a third
category since it can be performed on-demand
and purely client-side across frames without persistence,
combining aspects of both of the above categories."\\

@@

>>>>

\IEEEtitleabstractindextext{
\begin{abstract}
Some of the most dangerous web attacks, such as Cross-Site
Scripting and {\sc sql} injection, exploit vulnerabilities
in web applications that may accept and process
data of uncertain origin without proper validation or
filtering, allowing the injection and execution of
dynamic or domain-specific language code.
These attacks have been constantly topping the lists of
various security bulletin providers despite the numerous
countermeasures that have been proposed over the past 15 years.
In this paper, we provide an analysis on
various defense mechanisms against web code injection attacks.
We propose a model that highlights the key weaknesses enabling these attacks,
and that provides a common perspective for studying the available defenses.
We then categorize and analyze a set of 41 previously proposed defenses 
based on their accuracy, performance,
deployment, security, and availability characteristics.
Detection accuracy is of particular importance,
as our findings show that many defense
mechanisms have been tested in a poor manner. In addition, we observe
that some mechanisms can be bypassed by attackers with knowledge
of how the mechanisms work. Finally, we discuss the results
of our analysis, with emphasis on factors that may hinder
the widespread adoption of defenses in practice.
\vspace{-3mm}
\end{abstract}

@@

\noindent
Second note:
We also changed the caption of Table 1.\\

\noindent
{\bf Comment 2:} ``Admittedly, transition
from scientific research to real product
is challenging due to availability, usability,
performance and deployment issues.
Except for that, the paper does not thoroughly
discuss why many previous works
cannot stop attacks against web applications,
nor provide useful guidance on
how future research could improve upon existing works.
Are there any fundamental
limitations in previous works that make
them not suitable for defending against
some specific (if not all) attacks?
Can we integrate multiple solutions to build
stronger defense mechanisms?"\\

@@

\noindent
{\bf Response:}
We have updated our paper to include the
aforementioned mechanisms
(see Subsection 5.3, Figure 2 and 3).
The 3rd reviewer also
indicated that some representative
{\sc ifc} frameworks were missing.
Hence, we have added those too.
Note that,
those mechanisms are not
always easy to adopt because
developers need to learn new constructs
to utilize them.
We mention that in Subsection 6.4
(``Ease of Use").
Finally,
the addition of {\sc ifc} mechanisms
in our study affects many of our results
throughout Section 6 (``Observations").
Consequently,
we have updated this section too.\\

@@

\noindent
{\bf Comment 2:} ``Similarly, {\sc xss} is introduced
as an attack that has two forms,
reflected and persistent.
However,
even though it's mentioned later on,
how would {\sc dom}-based {\sc xss} fit into this breakdown?
I don't believe it does (neatly),
and I am of the view that it constitutes a third
category since it can be performed on-demand
and purely client-side across frames without persistence,
combining aspects of both of the above categories."\\

@@

\noindent
{\bf Response:}
The 2nd reviewer has also indicated that
information flow control solutions
were missing from our study.
Our paper now includes six solutions
that follow this approach
including {\sc sif}~\cite{CVMA07},
Hails~\cite{GLSTMMR12}
and Aeolus~\cite{CPSPBCCSL12}
(see Subsection 5.3, Figure 2 and 3).
Nevertheless,
we did not include Ur/Web~\cite{C10b}
in our study because it is a static 
analysis mechanism
(recall that we only consider defenses
that prevent attacks when they take place).

Note that,
most of these mechanisms were not
extensively tested in terms of security.
However,
such solutions do not need to be
established purely through testing,
since they provide systematic
arguments as to why their design is
secure against application attacks.
We stress this issue in Subsection
7.1 (``Improving Testing Accuracy").
Furthermore,
we discuss the usability issues of
{\sc ifc} solutions in Subsection 6.4
(``Ease of Use").

As we pointed out in our
response to the 2nd reviewer,
the addition of {\sc ifc} mechanisms
in our paper affects many of our results
throughout Section 6 (``Observations").
Consequently,
we have updated this section too.\\
